---
title: "Wentworth Puzzles"
subtitle: "GeoX Regional Test Results"
date-format: "DD-MM-YYYY"
description: "ITV Measurement Innovation"
title-block-banner: url(itv_background_crop.jpg)
title-block-banner-color: white
date: "Report Last Run: `r Sys.time()`"
mainfont: Verdana
sansfont: Georgia
format: 
  html:
    grid: 
      body-width: 1200px
    embed-resources: true
    smooth-scroll: true
    theme: cosmo
    fontcolor: black
    toc: true
    toc-location: left
    toc-title: Summary
    toc-depth: 4
---

```{r setup, include=FALSE}

knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)
library(geoxR)
library(GeoLift)
library(tidyverse)
library(baRb)
library(googleAnalyticsR)
library(googleCloudStorageR)
devtools::load_all(".")

ga_id <- 375877571

barb_name <- c("PLANT_MEAT")

report_title <- "This"

data_start <- '2023-09-01'
data_end <- '2023-12-11'
test_start <- '2023-10-16'
test_end <- '2023-12-10'

test_regions <- "London"

exclude_regions <- c(NA)

# test_start_n <- as.numeric(as.Date(test_start) - as.Date(data_start))
# data_end_n <- as.numeric(as.Date(data_end) - as.Date(data_start))

```
## Report Setup

Test start date: `r test_start`

Test end date: `r test_end`

Data end date: `r data_end`

Test region(s): `r test_regions`

## Campaign Summary

```{r spots}
#| layout-ncol: 2

# spots <- baRb::barb_get_spots(data_start, data_end, barb_name, metric = "tvrs")
# spots_impacts <- baRb::barb_get_spots(data_start, data_end, barb_name)
# 
# write_rds(spots, "spots.rds")
# write_rds(spots_impacts, "spots_impacts.rds")

spots <- read_rds("spots.rds")
spots_impacts <- read_rds("spots_impacts.rds")


spots_rollup <- spots_impacts |>
  dplyr::mutate(date = lubridate::floor_date(as_datetime(standard_datetime), "day")) |>
  dplyr::group_by(date, panel_region) |>
  dplyr::summarise(impacts = sum(all_adults)) |>
  dplyr::ungroup()

spots_rollup |>
  plotly::plot_ly(colors = as.character(itvPalette::itv_palette()[1:7])) |>
    plotly::add_bars(x = ~date, y = ~impacts, color = ~panel_region) |>
    plotly::layout(barmode = 'stack',
                   legend = list(x = 0, y = 100))

spots |>
  dplyr::group_by(panel_region) |>
  filter(stringr::str_detect(station_name, "ITV1")) |>
  summarise(all_adults = round(sum(all_adults), 0)) |>
  gt::gt() |>
    gt::cols_label(panel_region = "Region",
                   all_adults = "Adult TVR's") |>
    gtExtras::gt_theme_538()


```

```{r data_load, include=FALSE}

# Get Traffic
# all_traffic <- ga4_query(ga_id, data_start, data_end) |>
#   write_rds("all_traffic.RDS")
# 
# cpc_traffic <-
#   ga4_query(ga_id, data_start, data_end, filter_clause = ga4_filter_channel_group("Paid Search")) |>
#   write_rds("cpc_traffic.RDS")
# 
# organic_traffic <-
#   ga4_query(ga_id, data_start, data_end, filter_clause = ga4_filter_channel_group("Organic Search")) |>
#   write_rds("organic_traffic.RDS")
# 
# paid_social_traffic <-
#   ga4_query(ga_id, data_start, data_end, filter_clause = ga4_filter_channel_group("Paid Social")) |>
#   write_rds("paid_social_traffic.RDS")
# 
# direct_traffic <-
#   ga4_query(ga_id, data_start, data_end, filter_clause = ga4_filter_channel_group("Direct")) |>
#   write_rds("direct_traffic.RDS")
# 

# Load from cache
all_traffic <- read_rds("all_traffic.RDS")

# Calculate Geolifts for all sources
geolifts <- calculate_geoLifts(
  list("all_traffic" = all_traffic
       # # "cpc_traffic" = cpc_traffic,
       # "organic_traffic" = organic_traffic,
       # "paid_social_traffic" = organic_traffic,
       # "direct_traffic" = organic_traffic
       ),
  test_regions = test_regions,
  exclude_regions = exclude_regions,
  test_start = test_start,
  test_end = test_end,
  benchmark_advertiser = "Wentworth Puzzles",
  benchmark_comment = "First geo test, westcountry and Meridian",
  benchmark_schedule = spots_rollup
) |> 
  write_rds('geox.rds')

all_traffic_carryover <-
  uplift_ga_carryover(all_traffic,
            test_regions,
            campaign_start = test_start,
            campaign_end = test_end)

```

## All Web Traffic

Uplift: `r geolifts$all_traffic$inference$Perc.Lift`%

Probability uplift is zero: `r geolifts$all_traffic$summary$average_att$p_val`%

Synthetic control improvement over naive model: `r round((1 - geolifts$all_traffic$summary$scaled_l2_imbalance)*100, 0)`%

```{r}
#| layout-ncol: 2

geoLift_plotly_test_control(geolifts$all_traffic, data_start, test_start, "All Traffic")
geoLift_plotly_att(geolifts$all_traffic, data_start, test_start, "All Traffic")

```

